The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-27 article.tex
proofing

  Along with the new stereochemistry representation, algorithms were required in several areas. Generally
  a user does not need to invoked these procedures explicitly as they are called as needed within existing
  APIs:

@@

  A second new design goal was introduced to balance between size restrictions
  of some use cases, such as Java applets, and the rendering functionality. In
  particular, some functionality, even after Modularization, needed considerable
  parts of the CDK library, making creation if a small-sized applet unfeasible.
  Therefore, the rendering API was modularized to allow splitting up rendering
  functionality into modules, with varying CDK dependencies.

@@

  Aromaticity has seen many definitions in the past and for cheminformatics it
  frequently is algorithmically defined. The outcome of an aromaticity calculation
  depends on a number of atom type features and heuristics, which in literature
  often are not well defined. Based on this information several different
  algorithmic definitions of aromaticity can be defined. Older CDK versions had
  various models implemented and the code was scattered throughout the library.
  This was unified resulting in a three models, of which two are based on the
  CDK atom typer, to provide the number of electrons donated by each atom to
  the delocalized $\pi$ system. The difference between these two models is
  how double bonds pointing outwards from a ring are contributing.

>>>>

  Along with the new stereochemistry representation, algorithms were required in several areas. Generally
  a user does not need to invoke these procedures explicitly as they are called as needed within existing
  APIs:

@@

  A second new design goal was introduced to balance between size restrictions
  of some use cases, such as Java applets, and the rendering functionality. In
  particular, some functionality, even after Modularization, needed considerable
  parts of the CDK library, making creation of a small-sized applet unfeasible.
  Therefore, the rendering API was modularized to allow splitting up rendering
  functionality into modules, with varying CDK dependencies.

@@

  Aromaticity has seen many definitions in the past and for cheminformatics it
  frequently is algorithmically defined. The outcome of an aromaticity calculation
  depends on a number of atom type features and heuristics, which in literature
  often are not well defined. Based on this information several different
  algorithmic definitions of aromaticity can be defined. Older CDK versions had
  various models implemented and the code was scattered throughout the library.
  This was unified resulting in three models, of which two are based on the
  CDK atom typer, to provide the number of electrons donated by each atom to
  the delocalized $\pi$ system. The difference between these two models is
  how double bonds pointing outwards from a ring are contributing.
